\documentclass[9pt]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment. 

% \RequirePackage[english,slovene]{babel} % when writing in slovene
\RequirePackage[slovene,english]{babel} % when writing in english

\usepackage{todonotes}

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} = Template for a one-column mathematics article
% {pnasinvited} = Template for a PNAS invited submission

\selectlanguage{english}
% \selectlanguage{slovene}
% \etal{in sod.} % comment out when writing in english
% \renewcommand{\Authands}{ in } % comment out when writing in english
% \renewcommand{\Authand}{ in } % comment out when writing in english

\newcommand{\set}[1]{\ensuremath{\mathbf{#1}}}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\uvec}[1]{\ensuremath{\hat{\vec{#1}}}}
\newcommand{\const}[1]{{\ensuremath{\kappa_\mathrm{#1}}}}

\newcommand{\num}[1]{#1}

\graphicspath{{./fig/}}

\title{Collective Behaviour\\ Optimal Shepherding}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author{Franziska Weber}
\author{Franz Muszarsky}
\author{Kimberley Frings}

\affil{Final Report} 

% Please give the surname of the lead author for the running footer
% \leadauthor{Weber, Muszarsky, Frings} 

% Please add here a significance statement to explain the relevance of your work
% \significancestatement{This is the significance statement.}{add | some | keywords}

% Please include corresponding author, author contribution and author declaration information
%\authorcontributions{Please provide details of author contributions here.}
%\authordeclaration{Please declare any conflict of interest here.}
%\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
%\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
% \keywords{add | some | keywords} 

\begin{abstract}
Herding denotes a special type of so-called shepherding behaviours in which the shepherds try to steer to flock from a starting point to a target. We investigated the problem of finding optimal herding strategies by building upon an existing agent-based shepherding model. We extended this model by adding a surrounding fence to the environment and by considering the case where multiple shepherds are controlling the flock together. We also implemented an alternative algorithm for multiple shepherds and compared the performance of this algorithm to the one of our model. Our investigations revealed that in most cases the surrounding fence does not influence the shepherding process a lot and that the effect of introducing additional shepherds depends strongly on the behaviour of the flock. 

Our model is publicly available at \url{https://github.com/ki-mberley/Collective-Behaviour}.
\end{abstract}

\dates{\textbf{\today}}
\program{BM-RI}
\vol{2023/24}
\no{CB:GA} % group ID
%\fraca{FRIteza/201516.130}

\begin{document}

% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalised the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\input{introduction}

\section*{Methods}
\input{methods}

\section*{Results}
\label{sec:results}
\input{results}

\section*{Discussion}
\label{sec:discussion}
\input{discussion}

\section*{Conclusion and outlook}
\label{sec:conclusion}
\input{conclusion}

\acknow{
\textit{Franziska Weber} took care of the GitHub repository, researched existing models with multiple shepherds, wrote the description of the original model, analyzed the effect of introducing multiple shepherds, implemented the alternative agent-based shepherding algorithm and compared it to the optimization-based approach.
\textit{Kimberley Frings} corrected and initially executed the existing implementation, implemented the model extensions with a fence and multiple shepherds, composed all three reports and analyzed the effect of introducing a surrounding fence. \textit{Franz Muszarsky} created the presentation and the video. All three worked on understanding the implementation of the model and on the organization of the project.} 
\showacknow % Display the acknowledgments section

% \pnasbreak splits and balances the columns before the references.
% If you see unexpected formatting errors, try commenting out this line
% as it can run into problems with floats and footnotes on the final page.
%\pnasbreak

\begin{multicols}{2}
\section*{\bibname}
% Bibliography
\bibliography{bibliography}
\end{multicols}

\newpage

\section*{Appendix}
\label{sec:appendix}
\appendix
\input{appendix}

\end{document}








